Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : A review and a simple implementation for the wake of a cylinder

### 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_ASME---copie---copie.tex
minor fix

\usepackage{cprotect}

@@

The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics. Specific analytical and numerical methods suited to the description have emerged in the second part of the 19th century and continuously evolved up to the present day. When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}

@@

The objective of the present work is to contribute to the popularization of such methods 
in two ways:
%for both research and education purposes. 
\begin{itemize}
\item
First, we give a concise but self-contained exposition of the main concepts and 
specific numerical methods pertaining to global stability, including basic linear stability, adjoint-based sensitivity, as well as the most recent nonlinear developments.
\item
Secondly we offer an open-source and user-friendly software called  "StabFem"
\cprotect\footnote{The StabFem software may be obtained at the following url : 
\verb| https://github.com/erbafdavid/StabFem |} 
to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis. Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
\end{itemize}

@@

\begin{figure*}[t]
\small
\begin{lstlisting}
baseflow = SF_Init('Mesh_Cylinder_Large.edp');
baseflow = SF_BaseFlow(baseflow,'Re',1);
baseflow = SF_BaseFlow(baseflow,'Re',10);
baseflow = SF_BaseFlow(baseflow,'Re',60);
baseflow = SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
[ev,em] = SF_Stability(baseflow,'shift',0.04+0.74i,'type','S')
baseflow = SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.01);
plotFF(baseflow,'mesh'); plotFF(baseflow,'ux');

Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
    for Re = Re_Range
        baseflow = SF_BaseFlow(baseflow,'Re',Re);
        Drag_tab = [Drag_tab,baseflow.Drag];
        Lx_tab = [Lx_tab,baseflow.Lx];
    end
plot(Re_Range,2*Drag_tab,'b+-');
plot(Re_Range,Lx_tab,'b+-');

Re_Range = [40 : 2: 100];lambda_branch=[];
baseflow=SF_BaseFlow(baseflow,'Re',40);
[ev,em] = SF_Stability(baseflow,'shift',-.03+.72i,'nev',1,'type','D');
    for Re = Re_Range
        baseflow = SF_BaseFlow(baseflow,'Re',Re);
        [ev,em] = SF_Stability(baseflow,'nev',1,'shift','cont');
        lambda_branch = [lambda_branch ev];
    end
plot(Re_Range,real(lambda_branch),'b+-');
plot(Re_Range,imag(lambda_branch)/(2*pi),'b+-');
\end{lstlisting}
\normalsize
\caption{Illustration of the usage of the StabFem software to produce an adapted mesh and study the base flow and the linear stability properties of a cylinder
(from script {\em SCRIPT\_CYLINDER\_DEMO.m})}
\label{Listing2}
\end{figure*}

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_Mesh.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowRe60.png}
%\vspace{-1.cm}
\caption{Adapted mesh $(a)$  and base flow (axial velocity component) ($b$) for the flow over a cylinder at $Re=Re_c = 46.7$.}
\label{fig:Baseflow}
\end{figure}

@@

The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow. To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation. This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions. We have experimented two different ideas. The first is to adapt the mesh to the base flow and the structure of the leading eigenmode. A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity. Results show that the two procedures yield the same values for the eigenvalues with less than $1\%$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A). So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option. On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advised to use mesh adaptation on the eigenmode.

@@

@@

SECTION TO BE COMPLETED.

\paragraph{Problem description}

Cylinder of unit diameter (radius $r=1/2$), velocity $U = 1$ at inlet.

Domain dimension $[-40,80]x[0,40]$. No-stress conditions at outlet AND LATERAL BOUNDARY.

Definition of lift and drag operators :

\be{drag}
F_x ({\bf u},p) = 
 \int_{\Gamma_w} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} 
\ee

\be{lift}
F_y ({\bf u},p) = 
 \int_{\Gamma_w} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} 
\ee

\paragraph{Mesh adaptation procedure}

First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
Then we perform the mesh adaptation with the structural sensitivity, as explained in a previously (line 13). 
The resulting mesh is used for the rest of the computation presented in this paper (except for displaying the eigenmode in figure 4$a$). 
Appendix A presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $1\%$ accuracy for the eigenvalue, while requiring a very reasonable number of grid points compared to previous studies of this problem.

%It is shown that as well as doing mesh adaptation with the eigenmode structure instead of the sensitivity, as discussed above, gives comparable results within $1\%$ as for the eigenvalue of the most amplified mode.

%The produced outputs (lines 14-17) gives information about the resulting mesh. 
%Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake). Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19). Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).

@@

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeRe60.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjRe60.png}
%\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
%\vspace{-.5cm}
\caption{Eigenmode $(a)$  (axial velocity component),  Adjoint mode $(b)$ and structural sensitivity ($c$) for the cylinder's wake at $Re=Re_c = 46.7$.}
\label{fig:Eigenmode}
\end{figure}

@@

Figure \ref{fig:Eigenmode} : description of eigenmode.

Figure \ref{fig:SigmaOmega} : growth rates/Strouhal.

@@

@@

SECTION TO BE COMPLETED

@@

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Lift_Re_SC.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
\end{center}
\caption{Harmonic-balance results : characteristics of the limit cycle.
NOTE THAT THE AMPLITUDE IS NOTABLY LOWER THAN IN MANTIC-LUGO. TO BE EXPLAINED.
}
\label{fig:HB}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
\includegraphics[width=.9 \linewidth]{Cylinder_SC100_LiftSigma.png}
\end{center}
\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 100$. NOTE THAT THE AMPLITUDE IS NOTABLY LOWER THAN IN MANTIC-LUGO. TO BE EXPLAINED.}
\label{fig:SC100}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re_TESTMESHES.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_TESTMESHES.png}
\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_0)$ ($b$) as function of Reynolds number FOR 8 DIFFERENT MESHES}
\label{fig:MeshConvergence}
\end{figure}

@@

\begin{figure*}
\small
\begin{lstlisting}
> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','D');
> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);  
      ### ADAPT mesh to base flow AND MODE   ; InterpError = 0.005  ; Hmax = 10
      #   Number of points np = 13458 ; Ndof = 120030
      #  deltamin, deltapax : 0.0089891 , 13.367
      #  delta_(A,B,C,D) : 0.020536 , 0.082852 , 0.07316 , 0.11914
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
      # Base flow converged in 4 iterations ; Drag = 0.64695; Lx = 4.0715
      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
      # Stability calculation converged in 4 iterations, lambda = 0.047152+0.74808i.

> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);
      ### ADAPT mesh to base flow AND SENSITIVITY ; InterpError = 0.005  ; Hmax = 10
      #   Number of points np = 4355 ; Ndof = 38559
      #  deltamin, deltapax : 0.0058536 , 13.1164
      #  delta_(A,B,C,D) : 0.01049 , 0.091861 , 0.13319 , 0.89372
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
      # Base flow converged in 3 iterations ; Drag = 0.64758; Lx = 4.0725
      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
      # Stability calculation converged in 3 iterations (D+A+S), lambda = 0.047165+0.74823i.

\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
\end{figure*}

In this appendix we compare the results obtained with 8 different meshes, to demonstrate the efficency of the mesh adaptation process. The whole results can be obtained using the script {\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m} available in the StabFem repository.

The Reference mesh is adapted to the Structural sensitivity, for $Re= 60$, with interpolation error 0.01, mesh dimensions $[-40,120]\times[0,40]$, and no-stress boundary conditions at the outlet and lateral boundaries.

Figure \ref{fig:MeshConvergence} displays the results.

\begin{table}
$$
\begin{array}{c|c|c|c|c|c|c|}
\mbox{ Mesh } & N_p & N_{d.o.f} & \mbox{ Dimensions } & h_{min} & h_{wall} & h_{wake} \\ 
\mbox{ BaseFlow } & 1468 & 12856 \\
\mbox{ Ref.} & 2055 & 18105\\
\mbox{ Mode} &12308 & 109788 \\
\mbox{ Err= }0.005 & 4355 & 38559 \\
\mbox{Slip B.C.} & \\ 
\mbox{Larger} & \\
\mbox{Smaller} &  
\end{array}
$$
\caption{Description of the 8 different meshes used in the convergence study}
\end{table}

%Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
%and the output produced.

\section{Detail of the weak formulation}
%The problem can be set into weak form by multiplying by multiplying Eq. \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$. After a few integration by parts we are led to :

SECTION TO BE COMPLETED.

We have to explain the integration by parts of the viscous term.

\begin{eqnarray}
\label{NewtonWeak}
&\forall ({\bf v};q), \\
\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
\nonumber
\\
\nonumber
\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
+ \nabla \cdot {\bf u}_b^g  q 
- \nabla \cdot {\bf v} p_b^g
+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
\end{eqnarray}

>>>>

@@

The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics. Specific analytical and numerical methods suited to the description have emerged in the second part of the 19th century and continuously evolved up to the present day. When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."\footnote{Sorry Laurette !}

@@

The objective of the present work is to contribute to the popularization of such methods 
in two ways:
%for both research and education purposes. 
\begin{itemize}
\item
First, we give a concise but self-contained exposition of the main concepts and 
specific numerical methods pertaining to global stability, including basic linear stability, adjoint-based sensitivity, as well as the most recent nonlinear developments.
\item
Secondly we offer an open-source and user-friendly software called  "StabFem" to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis. Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
\end{itemize}

@@

@@

The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow. To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation. This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions. We have experimented two different ideas. The first is to adapt the mesh to the base flow and the structure of the leading eigenmode. A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity. Results show that the two procedures yield the same values for the eigenvalues with less than $1\percent$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A). So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option. On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advied to use mesh adaptation on the eigenmode.

@@

\begin{figure*}[t]
\small
\begin{lstlisting}
Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
    for Re = Re_Range
        baseflow = SF_BaseFlow(baseflow,'Re',Re);
        Drag_tab = [Drag_tab,baseflow.Drag];
        Lx_tab = [Lx_tab,baseflow.Lx];
    end
plot(Re_Range,2*Drag_tab,'b+-');
plot(Re_Range,Lx_tab,'b+-');

Re_Range = [40 : 2: 100];lambda_branch=[];
baseflow=SF_BaseFlow(baseflow,'Re',40);
[ev,em] = SF_Stability(baseflow,'shift',-.03+.72i,'nev',1,'type','D');
    for Re = Re_Range
        baseflow = SF_BaseFlow(baseflow,'Re',Re);
        [ev,em] = SF_Stability(baseflow,'nev',1,'shift','cont');
        lambda_branch = [lambda_branch ev];
    end
plot(Re_Range,real(lambda_branch),'b+-');
plot(Re_Range,imag(lambda_branch)/(2*pi),'b+-');
\end{lstlisting}
\normalsize
\caption{Illustration of the computation of base-flow properties with StabFem (from script)}
\label{Listing2}
\end{figure*}

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_Mesh.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowReC.png}
%\vspace{-1.cm}
\caption{Adapted mesh $(a)$  and base flow (axial velocity component) ($b$) for the flow over a cylinder at $Re=Re_c = 46.7$.}
\label{fig:Baseflow}
\end{figure}

@@

@@

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeReC.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjReC.png}
%\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityReC.png}
%\vspace{-.5cm}
\caption{Eigenmode $(a)$  (axial velocity component),  Adjoint mode $(b)$ and structural sensitivity ($c$) for the cylinder's wake at $Re=Re_c = 46.7$.}
\label{fig:Eigenmode}
\end{figure}

@@

%popular class of method are {\em power methods} which allow to compute a limited set

%based on the idea that the repeated application of an operator mostly amplifies the perturbations along the eigenspaces with largest eigenvalues.

%These de Andrea Fani

%\paragraph{Implementation and mesh adaptation for stability calculations}

Matlab driver...

%\paragraph{Sample results}

%\subsection{Illustration of the mesh adaptation for stability calculations}

%See listing....

%\subsection{Sample results for a cylinder}

\clearpage

@@

With $F_y ({\bf u_1}) = 
 \int_{\Gamma_w} \left[-p_1 {\bf n} + \frac{2}{Re} {\bf D}({\bf u_1}) \cdot {\bf n} \right]   \cdot {\bf e_y}  = 0.$

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Lift_Re_SC.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
\end{center}
\caption{Harmonic-balance results : mode characteristics}
\label{fig:HB}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
\includegraphics[width=.9 \linewidth]{Cylinder_SC100_LiftSigma.png}
\end{center}
\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 60$}
\label{fig:SC60}
\end{figure}

@@

@@

We illustrate the procedure in the case of a cylinder.  Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
and the output produced.
First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).

Then we perform the mesh adaptation (line 13). The produced outputs (lines 14-17) gives information about the resulting mesh. 
Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake). Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19). Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).

\begin{figure*}
\small
\begin{lstlisting}
\end{lstlisting}
\normalsize

\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
\label{listing3}
\end{figure*}

\section{Detail of the weak formulation}
The problem can be set into weak form by multiplying by multiplying Eq. \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$. After a few integration by parts we are led to :
\begin{eqnarray}
\label{NewtonWeak}
&\forall ({\bf v};q), \\
\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
\nonumber
\\
\nonumber
\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
+ \nabla \cdot {\bf u}_b^g  q 
- \nabla \cdot {\bf v} p_b^g
+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
\end{eqnarray}

### 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_ASME_5oct.tex
minor fix

To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow. 
The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.

The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow. To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation. This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions. We have experimented two different ideas. The first is to adapt the mesh to the base flow and the structure of the leading eigenmode. A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity. Results show that the two procedures yield the same values for the eigenvalues with less than $1\percent$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A). So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option. On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advied to use mesh adaptation on the eigenmode.

In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation 
(to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.

@@

@@

\section{Detail of the weak formulation}
The problem can be set into weak form by multiplying by multiplying Eq. \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$. After a few integration by parts we are led to :
\begin{eqnarray}
\label{NewtonWeak}
&\forall ({\bf v};q), \\
\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
\nonumber
\\
\nonumber
\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
+ \nabla \cdot {\bf u}_b^g  q 
- \nabla \cdot {\bf v} p_b^g
+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
\end{eqnarray}

>>>>

To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow. 
The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
In our implementation, the whole process is performed using the Matlab driver
 {\em Freefem\_AdaptMesh.m}.

@@

\paragraph{Problem description}

We will now illustrate the

\paragraph{Mesh adaptation procedure}

@@

\section{Detail of the weak formulation}
%The problem can be set into weak form by multiplying by multiplying Eq. \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$. After a few integration by parts we are led to :
\begin{eqnarray}
\label{NewtonWeak}
&\forall ({\bf v};q), \\
\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
\nonumber
\\
\nonumber
\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
+ \nabla \cdot {\bf u}_b^g  q 
- \nabla \cdot {\bf v} p_b^g
+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
\end{eqnarray}
